Lesson 5
========================================================
```{r, warning=FALSE}
library(ggplot2)
library(dplyr)
pf <- read.csv(file = "pseudo_facebook.tsv", sep = "\t")
```

***

### Third Qualitative Variable
Notes: Create a new dataset with  summary stats features using dplyr and pipe operator %>% 

```{r Third Qualitative Variable}
#ggplot(aes(x = gender, y = age),
#       data = subset(pf, !is.na(gender))) + geom_histogram()

# Write code to create a new data frame,
# called 'pf.fc_by_age_gender', that contains
# information on each age AND gender group.

# The data frame should contain the following variables:

#    mean_friend_count,
#    median_friend_count,
#    n (the number of users in each age and gender grouping)

# Note that if you are grouping by
# more than one variable, you will probably need to call the
# ungroup() function. 

pf.fc_by_age_gender <- pf %>% 
  filter(!is.na(gender)) %>%
  group_by(age, gender) %>%
  summarise( mean_friend_count = round(mean(friend_count), 4), 
             median_friend_count = round(median(friend_count),0), 
             n = n()) %>% 
  ungroup(age) %>%
  arrange(age)
#summarise will ungroup one variable i.e., gender, use ungroup to another variable. 
```

***

### Plotting Conditional Summaries
Notes:Median friend count for each gender by age. 

```{r Plotting Conditional Summaries}
# Create a line graph showing the
# median friend count over the ages
# for each gender. Be sure to use
# the data frame you just created,
# pf.fc_by_age_gender.

ggplot(data = pf.fc_by_age_gender, aes(x = age, y = mean_friend_count)) + 
  geom_line(stat = "identity", aes(color = gender))

```

***

### Thinking in Ratios
Notes:

***

### Wide and Long Format
Notes:

***

### Reshaping Data
Notes:

```{r, warning=FALSE}
if(require("reshape2")) {
  install.packages("reshape2")
}
library(reshape2)

pf.fc_by_age_gender.wide <- dcast(data = pf.fc_by_age_gender, age ~ gender, 
                                  value.var = "median_friend_count")
```


***

### Ratio Plot
Notes:

```{r Ratio Plot}
# Plot the ratio of the female to male median
# friend counts using the data frame
# pf.fc_by_age_gender.wide.

# Think about what geom you should use.
# Add a horizontal line to the plot with
# a y intercept of 1, which will be the
# base line. Look up the documentation
# for geom_hline to do that. Use the parameter
# linetype in geom_hline to make the
# line dashed.

# The linetype parameter can take the values 0-6:
# 0 = blank, 1 = solid, 2 = dashed
# 3 = dotted, 4 = dotdash, 5 = longdash
# 6 = twodash

ggplot(data = pf.fc_by_age_gender.wide, aes(x = age, y = female/male)) + 
  geom_line(stat = "identity") + 
  geom_hline(yintercept = 1, linetype = 3) + 
  labs(y = "female by male ratio")

```

***

### Third Quantitative Variable
Notes:

```{r Third Quantitative Variable}
tail(round(pf$tenure/365, 2) , 8)
tail((pf$tenure + (365 - (pf$tenure%%365)))/365, 8)
#head(365 - (pf$tenure%%365) , 50)
##hard way
pf$year_joined <- ifelse(pf$tenure%%365 == 0, 2014 - pf$tenure/365,  2014 - (pf$tenure + (365 - pf$tenure%%365))/365 )
#another way using floor
pf$year_joined_fl <- floor(2014 - pf$tenure/365)
head(pf[, c("year_joined", "year_joined_fl")], 50)
pf$compare <- ifelse(pf$year_joined == pf$year_joined_fl, T, F)
table(pf$compare)
pf[pf$compare == F, c("tenure","year_joined", "year_joined_fl")]
table(pf$year_joined)
pf <- pf %>% select(-c(year_joined_fl, compare))
```

***

### Cut a Variable
Notes:

```{r Cut a Variable}
# Create a new variable in the data frame
# called year_joined.bucket by using
# the cut function on the variable year_joined.

# You need to create the following buckets for the
# new variable, year_joined.bucket

#        (2004, 2009]
#        (2009, 2011]
#        (2011, 2012]
#        (2012, 2014]

# Note that a parenthesis means exclude the year and a
# bracket means include the year.

#y <- cut(x = c(1,2,3,4,5), breaks = c(1:2, 3:4))
yj_buckets <- c(2004:2009, 2009:2011, 2011:2012, 2012:2014)
pf$year_joined.bucket <- cut(x = pf$year_joined, 
                             breaks = 
                               c(2004, 2009, 2011, 2012, 2014))

table(pf$year_joined.bucket)

```

***

### Plotting it All Together
Notes:

```{r Plotting it All Together}
# Create a line graph of friend_count vs. age
# so that each year_joined.bucket is a line
# tracking the median user friend_count across
# age. This means you should have four different
# lines on your plot.

# You should subset the data to exclude the users
# whose year_joined.bucket is NA.

ggplot(data = subset(x = pf, subset = !is.na(pf$year_joined.bucket)), 
       aes(y = friend_count, x = age)) + 
  geom_line(aes(color = year_joined.bucket), 
            stat = "summary", fun.y = median) 
  
```

***

### Plot the Grand Mean
Notes:

```{r Plot the Grand Mean}
# Write code to do the following:

# (1) Add another geom_line to code below
# to plot the grand mean of the friend count vs age.

# (2) Exclude any users whose year_joined.bucket is NA.

# (3) Use a different line type for the grand mean.

ggplot(data = subset(x = pf, subset = !is.na(pf$year_joined.bucket)), 
       aes(y = friend_count, x = age)) + 
  geom_line(aes(color = year_joined.bucket), 
            stat = "summary", fun.y = median) +
  geom_line(stat = "summary", fun.y = mean, linetype = 2)

```

***

### Friending Rate
Notes:

```{r Friending Rate}
pf_tenure <- subset(pf, tenure > 0 )
pf_tenure$friend_rate <- pf_tenure$friend_count/pf_tenure$tenure
summary(pf_tenure$friend_rate)
with(data = subset(pf, tenure >= 1), expr = summary(friend_count/tenure))
```

***

### Friendships Initiated
Notes:

What is the median friend rate?  0.2205

What is the maximum friend rate?  417.0000 

```{r Friendships Initiated}
# Create a line graph of mean of friendships_initiated per day (of tenure)
# vs. tenure colored by year_joined.bucket.

# You need to make use of the variables tenure,
# friendships_initiated, and year_joined.bucket.
tail(pf[,c("friendships_initiated", "tenure", "year_joined.bucket")])

ggplot(data = pf_tenure, aes(x = tenure, y =  friendships_initiated/tenure)) + 
  geom_line(aes(color = year_joined.bucket), stat = "summary", fun.y = mean)

ggplot(data = pf_tenure, aes(x = tenure, y =  friendships_initiated/tenure)) + 
  geom_smooth(aes(color = year_joined.bucket))

```

***

### Bias-Variance Tradeoff Revisited
Notes:

```{r Bias-Variance Tradeoff Revisited}

ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean) 

ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

```

***

### Sean's NFL Fan Sentiment Study
Notes:

***

### Introducing the Yogurt Data Set
Notes:

***

### Histograms Revisited
Notes:

```{r Histograms Revisited}
yo <- read.csv(file = "yogurt.csv")
str(yo)
head(yo)
#change id to factor 
yo$id <- factor(yo$id)
str(yo)
ggplot(data = yo, aes(x = price)) + 
  geom_histogram(binwidth = 2) + 
  scale_x_continuous(breaks = seq(12,80,2))

```
Noticed: Yogurts priced between $66 - $70 are sold most. 
For binwidth of $2 the price variance is noticeable. 

***

### Number of Purchases
Notes:

```{r Number of Purchases}
print(paste0("Variety of prices: " , length(unique(yo$price))))
table(yo$price)
# Create a new variable called all.purchases,
# which gives the total counts of yogurt for
# each observation or household.
yo$all.purchases <- yo$strawberry + yo$blueberry + 
  yo$pina.colada + yo$plain + yo$mixed.berry

#or use transform

yo <- transform(yo, all.purchases = strawberry + blueberry + pina.colada + 
                  plain + mixed.berry)
summary(yo$all.purchases)
table(yo$all.purchases)
sum(complete.cases(yo$all.purchases))
```

***

### Prices over Time
Notes:

```{r Prices over Time}
# Create a scatterplot of price vs time.

# This will be an example of a time series plot.

# Resolve overplotting issues by using
# techniques you learned in Lesson 4.
ggplot(data = yo, aes(x = time, y = price)) +
  geom_point(aes(color = all.purchases), alpha = 1/4, shape = 21)
#alternatively use jitter
```

***

### Sampling Observations
Notes:

***

### Looking at Samples of Households

```{r Looking at Sample of Households}
set.seed(4230)
sample.ids <- sample(x = yo$id, size = 16)

ggplot(data = subset(yo, id %in% sample.ids), aes(x = time, y = price)) +
  
```

***

### The Limits of Cross Sectional Data
Notes:

***

### Many Variables
Notes:

***

### Scatterplot Matrix
Notes:

***

### Even More Variables
Notes:

***

### Heat Maps
Notes:

```{r}
nci <- read.table("nci.tsv")
colnames(nci) <- c(1:64)
```

```{r}
nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)

ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```


***

### Analyzing Three of More Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

