Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}
pf <- read.csv(file = "pseudo_facebook.tsv", sep = "\t")
library(ggplot2)
ggplot(data = pf, aes(x = age, y = friend_count)) + 
  geom_point() + 
  coord_cartesian(xlim = c(13,90))
```

***

#### What are some things that you notice right away?
Response:     
1. Friend count peaks for below 25 and at the age of around 70. 
2. No data for below 13 as that might be the legal limit of facebook account. 

***

### ggplot Syntax
Notes:

```{r ggplot Syntax}
ggplot(data = pf, aes(x = age, y = friend_count)) + 
  geom_jitter(alpha = 1/20) + 
  coord_cartesian(xlim = c(13,90))
```

***

### Overplotting
Notes:

```{r Overplotting}
ggplot(data = pf, aes(x = age, y = sqrt(friend_count))) + 
  geom_point() + 
  coord_cartesian(xlim = c(13,90)) 
#+ coord_trans(y = 'sqrt')
```

```{r, warning=FALSE}
# Examine the relationship between
# friendships_initiated (y) and age (x)
# using the ggplot syntax.

# We recommend creating a basic scatter
# plot first to see what the distribution looks like.
# and then adjusting it by adding one layer at a time.

# What are your observations about your final plot?

# Remember to make adjustments to the breaks
# of the x-axis and to use apply alpha and jitter.

ggplot(data = pf, aes(x = age, y = sqrt(friendships_initiated))) + 
  geom_jitter(alpha = 1/10) + 
  coord_cartesian(xlim = c(10,90)) + 
  scale_x_continuous(limits = c(10,90), breaks = seq(10,90,10))
```


#### What do you notice in the plot?
Response: Friends initiation is highest for below 30 and at around 70. 

***

### Coord_trans()
Notes:

```{r Coord_trans()}
ggplot(data = pf, aes(x = age, y = friend_count)) + 
  geom_point() + 
  coord_cartesian(xlim = c(13,90)) + 
  coord_trans(y = 'sqrt')
### I am not sure coord_trans is working. 
```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r, warning=FALSE}
# Plot mean friend count vs. age using a line graph.
# Be sure you use the correct variable names
# and the correct data frame. You should be working
# with the new data frame created from the dplyr
# functions. The data frame is called 'pf.fc_by_age'.

# Use geom_line() rather than geom_point to create
# the plot. You can look up the documentation for
# geom_line() to see what it does.

# ENTER ALL OF YOUR CODE TO CREATE THE PLOT BELOW THIS LINE.
# ===========================================================
ggplot(data = pf, aes(x =  age , y = friend_count)) + 
  geom_line() + 
  scale_x_continuous(limits = c(13,90))

```

#### What do you notice?
We don't have age in continous manner. 
***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}
#jitther with 1 alpha = 20 points 
ggplot(data = pf, aes(x = age, y = friend_count)) + 
  geom_jitter(alpha = 1/20, color = 'blue') + 
  coord_cartesian(xlim = c(13,90))
```

***

### Overplotting and Domain Knowledge
Notes: density of friend counts for each age. 

***

### Conditional Means
Notes:

```{r Conditional Means}
library(dplyr)
rm(pf.fc_by_age)
pf.fc_by_age <- pf %>% 
  group_by(age) %>%
  summarise(friend_count_mean = mean(friend_count), 
            friend_count_median = median(friend_count), 
            count = n()) %>% 
  arrange(age)
  
head(pf.fc_by_age)
```

Create your plot!

```{r Conditional Means Plot}
ggplot(data = pf, aes(x = age, y = sqrt(friend_count))) + 
  geom_point(alpha = 1/20, color = 'blue') + 
  coord_cartesian(xlim = c(13,90)) + 
  geom_line(stat = 'summary', fun.y = mean, color = 'red', show.legend = T) + 
  geom_line(stat = 'summary', fun.y = mean, color = 'dark green')
```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}

```

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}

```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(                 , cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}

```

***

### Strong Correlations
Notes:

```{r Strong Correlations}

```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
```

Create your plot!

```{r Temp vs Month}

```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}

```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}

```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}

```

***

### Age with Months Means

```{r Age with Months Means}

```

Programming Assignment
```{r Programming Assignment}

```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

