Lesson 3
========================================================

***

### What to Do First?
Notes:
Ask questions!
***

### Pseudo-Facebook User Data
Notes:

```{r Pseudo-Facebook User Data}
pf = read.csv(file = 'pseudo_facebook.tsv', sep = '\t')
head(pf)
```

***

### Histogram of Users' Birthdays
Notes:

```{r Histogram of Users\' Birthdays}
#install.packages('ggplot2')
library(ggplot2)
#install.packages('ggthemes', dependencies = TRUE)
library('ggthemes')
ggplot(data = pf, aes(x = pf$dob_day)) +
  geom_histogram(bins = 30, color = 'dark red', fill = 'light blue')
```

***

#### What are some things that you notice about this histogram?
Response: Many people has left 1st as their DOB Day. 

***

### Moira's Investigation
Notes:She feels the same ! 

***

### Estimating Your Audience Size
Notes: 

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response: Yoga camp

#### How many of your friends do you think saw that post?
Response: 100

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response: 10%

***

### Perceived Audience Size
Notes:

***
### Faceting
Notes:

```{r Faceting}
ggplot(data = pf, aes(x = pf$dob_day)) +
  geom_histogram(bins = 30) +
  facet_wrap( ~ pf$dob_month, ncol = 3)
```

#### Let’s take another look at our plot. What stands out to you here?
Response: January 1st 

***

### Be Skeptical - Outliers and Anomalies
Notes:

***

### Moira's Outlier
Notes:
#### Which case do you think applies to Moira’s outlier?
Response: January 1st 

***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
ggplot(data = pf, aes(x = pf$friend_count)) + 
  geom_histogram(bins = 100)

```

#### How is this plot similar to Moira's first plot?
Response: Skewed towards left

***

### Limiting the Axes
Notes:

```{r Limiting the Axes}
ggplot(data = pf, aes(x = pf$friend_count)) + 
  geom_histogram(binwidth = 10) + 
  scale_x_continuous(limits = c(0,1000))
```

### Exploring with Bin Width
Notes:

***

### Adjusting the Bin Width
Notes:

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
qplot(x = friend_count, data = pf, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))
```

***

### Omitting NA Values
Notes:

```{r Omitting NA Values}
ggplot(data = pf, aes(x = pf$friend_count)) +
  geom_histogram(binwidth = 10) + 
  scale_x_continuous(limits = c(0,1000), breaks = seq(0,1000,50)) +
  facet_wrap( ~ pf$gender)
pf_na = subset(pf, !is.na(pf$gender))
ggplot(data = pf_na, aes(x = pf_na$friend_count)) +
  geom_histogram(binwidth = 10) + 
  scale_x_continuous(limits = c(0,1000), breaks = seq(0,1000,50)) +
  facet_wrap( ~ pf_na$gender)
pf_na = na.omit(pf)  
ggplot(data = pf_na, aes(x = pf_na$friend_count)) +
  geom_histogram(binwidth = 10) + 
  scale_x_continuous(limits = c(0,1000), breaks = seq(0,1000,50)) +
  facet_wrap( ~ pf_na$gender)
```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}
summary(pf$gender)
by(data = pf$friend_count, INDICES = pf$gender, FUN = summary)
```

#### Who on average has more friends: men or women?
Response:Women, ofcourse!

#### What's the difference between the median friend count for women and men?
Response:22


#### Why would the median be a better measure than the mean?
Response:Robust to outlieners 

***

### Tenure
Notes:

```{r Tenure}
ggplot(data = pf[!is.na(pf$gender),], aes(x = tenure )) +
  geom_histogram(binwidth = 50, color = "dark red", fill = "orange") + 
  scale_x_continuous(limits = c(0, 2500), breaks = seq(0,2500,100))

```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}
ggplot(data = pf[!is.na(pf$gender),], aes(x = tenure/365 )) +
  geom_histogram(binwidth = .25, color = "dark red", fill = "orange") + 
  scale_x_continuous(limits = c(0, 10), breaks = seq(0,10,1))
```

***

### Labeling Plots
Notes:

```{r Labeling Plots}
ggplot(data = pf[!is.na(pf$gender),], aes(x = tenure/365 )) +
  geom_histogram(binwidth = .25, color = "dark red", fill = "orange") + 
  scale_x_continuous(limits = c(0, 10), breaks = seq(0,10,1)) +
  labs(title = "facebook yearly tenure", x = "Tenure in years", y = 'Users Count')
```

***

### User Ages
Notes:

```{r User Ages}
ggplot(aes(x = age), data = pf) +
  geom_histogram(binwidth = 1, fill = '#5760AB', color = 'black') +
  scale_x_continuous(breaks = seq(0, 113, 5))
```

#### What do you notice?
Response:

***

### The Spread of Memes
Notes:

***

### Lada's Money Bag Meme
Notes:

***

### Transforming Data
Notes: Engagement variables with higher magnitude of data. Transform the data by using log or square root. 
May be turn into normal distribution or known distribution. 

***

### Add a Scaling Layer
Notes: To avoid log of zero, add one to values before applying log. 
http://ggplot2.tidyverse.org/reference/scale_continuous.html 
```{r Add a Scaling Layer}
ggplot(data = pf, aes(x = friend_count)) + 
  geom_histogram(binwidth = 50, color = 'black', fill = 'light blue') + 
  scale_x_continuous(limits = c(0,1000), breaks = seq(0, 1000, 100)) + 
  labs( title = 'Friend Count without Transformation')

ggplot(data = pf, aes(x = friend_count )) + 
  geom_histogram( color = 'black', fill = 'light blue') + 
  scale_x_log10() + 
  labs(title = 'Friend Count with Log Transformation')

ggplot(data = pf, aes(x = friend_count )) + 
  geom_histogram( color = 'black', fill = 'light blue') + 
  scale_x_sqrt() + 
  labs(title = 'Friend Count with Log Transformation')

###All independent plot in one canvas
#install.packages("gridExtra", dependencies = T)
library(gridExtra)
p1 = ggplot(data = pf, aes(x = friend_count)) + 
  geom_histogram( color = 'black', fill = 'light blue') +
  scale_x_continuous(limits = c(0,1000))
p2 = ggplot(data = pf, aes(x = log10(friend_count + 1))) + 
  geom_histogram( color = 'black', fill = 'yellow')
p3 = ggplot(data = pf, aes(x = sqrt(friend_count))) + 
  geom_histogram( color = 'black', fill = 'light green') +
  scale_x_continuous(limits = c(0,40))
grid.arrange(p1, p2, p3, ncol = 1)
```

***


### Frequency Polygons

```{r Frequency Polygons, warning=FALSE}
ggplot(aes(x = friend_count, y = ..count../sum(..count..)),
  data = subset(pf, !is.na(gender))) +
  geom_freqpoly(aes(color = gender), binwidth=10) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) +
  xlab('Friend Count') +
  ylab('Proportion of users with that friend count')
```

***

### Likes on the Web
Notes:

```{r Likes on the Web, warning=FALSE}
ggplot(data = pf_na, aes(x = www_likes, y = ..count../sum(..count..))) + 
  geom_freqpoly(aes(color = gender)) + 
  scale_x_continuous(limits = c(-100,200)) +
  scale_x_log10() +
  xlab('Friend Count') +
  ylab('Proportion of users with Age')
```

### Who has more like, males or female?

```{r}
likes4females = sum(pf[pf$gender == 'female' & !is.na(pf$gender),]$www_likes)
likes4males = sum(pf[pf$gender == 'male' & !is.na(pf$gender),]$www_likes)
sprintf("Total Men likes = %s", likes4males)
sprintf("Total Women like = %s", likes4females)
sprintf("Total Women likes with by = %s", by(data = pf$www_likes, INDICES = pf$gender, FUN = sum)[1])
sprintf("Total Men likes with by = %s", by(data = pf$www_likes, INDICES = pf$gender, FUN = sum)[2])

```


***

### Box Plots
Notes:

```{r Box Plots}
ggplot(data = pf_na, aes(x = gender, y = friend_count)) + 
  geom_boxplot(color = 'dark red', fill = 'yellow')
```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.
Did you use the ylim parameter?
```{r, warning=FALSE}
ggplot(data = pf_na, aes(x = gender, y = friend_count)) + 
  geom_boxplot(color = 'dark red', fill = 'yellow') +
  scale_y_continuous(limits = c(0,1000))

```

```{r}
ggplot(data = pf_na, aes(x = gender, y = friend_count)) + 
  geom_boxplot(color = 'dark red', fill = 'yellow') +
  ylim(c(0,1000))
```

```{r}
ggplot(data = pf_na, aes(x = gender, y = friend_count)) + 
  geom_boxplot(color = 'dark red', fill = 'yellow') +
  coord_cartesian(ylim = c(0,1000))
```


***

### Box Plots, Quartiles, and Friendships
Notes:

```{r Box Plots, Quartiles, and Friendships}
ggplot(data = pf_na, aes(x = gender, y = friendships_initiated)) +
  geom_boxplot(color = 'dark green', fill = 'orange') + 
  coord_cartesian(ylim = c(0,150))
```

#### On average, who initiated more friendships in our sample: men or women?
Response:female
#### Write about some ways that you can verify your answer.
Response:Median and middle 50% is high for female. 
```{r Friend Requests by Gender}

```

Response:

***

### Getting Logical
Notes:

```{r Getting Logical}
pf$check_in <- ifelse(pf$likes > 0, 1, 0)
pf$check_in <- factor(pf$check_in)
pf$mobile_check_in <- ifelse(pf$mobile_likes > 0, 1, 0)
pf$mobile_check_in <- factor(pf$mobile_check_in)
(table(pf$mobile_check_in)/table(pf$check_in))*100
```

Response:

***

### Analyzing One Variable
Reflection:

***

***


***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!